quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays

### 2025-02-12 man/manuscript/softwareX_submission.tex
Updated submission.

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%\usepackage{lineno}

@@

\begin{document}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}

@@

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

@@

\author[label1,label2,label3]{Gage Rowden\corref{cor}\fnref{email}}
\ead{rowde002@umn.edu}
\fntext[email]{}
\cortext[cor]{}
\author[label1,label2,label3]{Peter Larsen}
\address[label1]{Department of Veterinary and Biomedical Sciences, University of Minnesota, St. Paul, MN 55108, USA.}
\address[label2]{Minnesota Center for Prion Research and Outreach, University of Minnesota, St. Paul, MN 55108, USA.}
\address[label3]{Priogen Corp., St. Paul, MN 55114, USA.}

@@

\section*{Metadata}
\label{}
\textit{The ancillary data table~\ref{codeMetadata} is required for the sub-version of the codebase. Please replace the italicized text in the right column with the correct information about your current code and leave the left column untouched.}

\begin{table}[ht]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata} \\
\hline
C1 & Current code version & V2.1.0 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/gage1145/quicR} \\
\hline
C3  & Permanent link to Reproducible Capsule & \url{https://github.com/gage1145/quicR/releases/tag/v2.1.0}\\
\hline
C4 & Legal Code License   & GPL-3 \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & R \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0) \\
\hline
C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf} \\
\hline
C9 & Support email for questions & rowde002@umn.edu\\
\hline
\end{tabular}
\caption{Code metadata}
\label{codeMetadata} 
\end{table}

@@

    In addition to analytical tools, quicR provides flexible and customizable visualization capabilities. Leveraging the powerful ggplot2 library \cite{ggplot2016}, quicR enables users to generate high-quality, publication-ready figures. These visualizations can be further customized using the intuitive '+' syntax of ggplot2, allowing for tailored presentations of RT-QuIC data.

@@

\textit{In this section, we want you to introduce the scientific background and the motivation for developing the software.}

\begin{itemize}
    \item \textit{Explain why the software is important and describe the exact (scientific) problem(s) it solves.}
    \item \textit{Indicate in what way the software has contributed (or will contribute in the future) to the process of scientific discovery; if available, please cite a research paper using the software.}
    \item \textit{Provide a description of the experimental setting. (How does the user use the software?)}
    \item \textit{Introduce related work in literature (cite or list algorithms used, other software etc.).}
\end{itemize}

@@

\section{Impact}
\textit{This is the main section of the article and reviewers will weight it appropriately.
Please indicate:}
\begin{itemize}
    \item \textit{Any new research questions that can be pursued as a result of your software.}
    \item \textit{In what way, and to what extent, your software improves the pursuit of existing research questions.}
    \item \textit{Any ways in which your software has changed the daily practice of its users.}
    \item \textit{How widespread the use of the software is within and outside the intended user group (downloads, number of users if your software is a service, citable publications, etc.).}
    \item \textit{How the software is being used in commercial settings and/or how it has led to the creation of spin-off companies.}
    \end{itemize}
% \textit{Please note that points 1 and 2 are best demonstrated by
%   references to citable publications.}

>>>>

%% The amssymb package provides various useful mathematical symbols
%% \usepackage{amssymb}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
% \usepackage{lineno}

@@

\begin{document}

\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}

@@

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

@@

\author[label1,label2,label3]{Gage Rowden\corref{cor}}
\fntext[ ]{\textit{E-mail address: }rowde002@umn.edu}
\cortext[cor]{Corresponding author.}
\author[label1,label2,label3]{Peter Larsen}
\address[label1]{Department of Veterinary and Biomedical Sciences, University of Minnesota, USA.}
\address[label2]{Minnesota Center for Prion Research and Outreach, University of Minnesota, USA.}
\address[label3]{Priogen Corp., USA.}

@@

\section*{Metadata}

\begin{table}[ht]
    \fontsize{9}{9}\selectfont
    \begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
        \hline
        \textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata} \\
        \hline
        C1 & Current code version & V2.1.0 \\
        \hline
        C2 & Permanent link to code/repository used for this code version & \url{https://github.com/gage1145/quicR} \\
        \hline
        C3  & Permanent link to Reproducible Capsule & \url{https://github.com/gage1145/quicR/releases/tag/v2.1.0}\\
        \hline
        C4 & Legal Code License & GPL-3 \\
        \hline
        C5 & Code versioning system used & git \\
        \hline
        C6 & Software code languages, tools, and services used & R \\
        \hline
        C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0) \\
        \hline
        C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf} \\
        \hline
        C9 & Support email for questions & rowde002@umn.edu\\
        \hline
    \end{tabular}
\caption{Code metadata}
\label{codeMetadata} 
\end{table}

@@

    In addition to analytical tools, quicR provides flexible and customizable visualization capabilities. Leveraging the powerful ggplot2 library \cite{ggplot2016}, quicR enables users to generate high-quality, publication-ready figures. These visualizations can be further customized using the intuitive `+' syntax of ggplot2, allowing for tailored presentations of RT-QuIC data.

@@

% \textit{In this section, we want you to introduce the scientific background and the motivation for developing the software.}
% 
% \begin{itemize}
%     \item \textit{Explain why the software is important and describe the exact (scientific) problem(s) it solves.}
%     \item \textit{Indicate in what way the software has contributed (or will contribute in the future) to the process of scientific discovery; if available, please cite a research paper using the software.}
%     \item \textit{Provide a description of the experimental setting. (How does the user use the software?)}
%     \item \textit{Introduce related work in literature (cite or list algorithms used, other software etc.).}
% \end{itemize}

@@

\section{Impact}
% \textit{This is the main section of the article and reviewers will weight it appropriately.
% Please indicate:}
% \begin{itemize}
%     \item \textit{Any new research questions that can be pursued as a result of your software.}
%     \item \textit{In what way, and to what extent, your software improves the pursuit of existing research questions.}
%     \item \textit{Any ways in which your software has changed the daily practice of its users.}
%     \item \textit{How widespread the use of the software is within and outside the intended user group (downloads, number of users if your software is a service, citable publications, etc.).}
%     \item \textit{How the software is being used in commercial settings and/or how it has led to the creation of spin-off companies.}
%     \end{itemize}
% \textit{Please note that points 1 and 2 are best demonstrated by
%   references to citable publications.}
